---
title: "Exercise 1"
author: "Marie Gleichauf, Chelsea Matthews, Hope Knopf"
date: "8/8/2018"
output: html_document
---

#Exercise 1

##Probaility Practice

###Part A
We need P(yes|truthful clickers) 
WE know:
P(yes) = .65
P(no) = .35
P(random clickers) = 0.3
P(truthful clikers) = 1-P(random clickers) = 1-0.3 = 0.7
P(yes|random clicker) = P(no|random clicker) = 0.5

P(Y) = P(Y|truthfull clickers) \* P(truthful clickers) + P(Y|random clickers)*P(random clickers)

.65 = P(yes|truthful clickers)*0.7 + 0.5(0.3)
P(yes|truthful clickers) = ((0.5)(0.3)-.65)/-0.7 
P(yes|truthful clickers) = 0.7142857

About 71% of the truthful clickers answered yes. 

###Part B
D = someone has disease
H = someone does not have disease (healthy)
P = positive test results
N = negative test results

we need P(D|P)
we have:
P(D) = 0.000025
P(H) = 1-P(D) = 1-0.000025 = 0.999975
P(P|D) = .993
P(N|H) = 0.9999 
P(P|H) = 1-0.9999=.0001 

P(P) = P(P|D)P(D) + P(P|H)P(H)
     =(.993\*0.000025) + (.0001*0.999975)
P(P) = 0.0001248225

Using Bayes 
P(D|P) = (P(D)*P(P|D))/P(P)
       = (0.000025*.993)/0.0001248225
P(D|P) =  0.1988824

So the probability that a person has the disease given that they test positive is about 20%. The low accuracy of this test could present numerous problems and lead to expensive further testing and cautionary treatments to people who don't actually have the disease. 

##Exploratory Analysis: Green Buildings
```{r message=FALSE, warning=FALSE}
library(mosaic)

green = read.csv('~/Documents/UT/Summer Classes/Intro to Predictive Modeling/Part 2/HW 1/greenbuildings.csv')

attach(green)
summary(green)
```

```{r}
green=green[green$leasing_rate>10,] #remove low occupancy
```

```{r}
rent_green = lm(Rent~., data = green)
summary(rent_green)
```
Running a linear regression gave us an indication of which variables could affect rent prices.

```{r}
#take subset of green and not green buildings
green_building = subset(green, green_rating==1)
dim(green_building)

non_green_building=subset(green, green_rating!=1)
dim(non_green_building)
```

```{r}
#amenities
green_building_amenities = subset(green_building, amenities==1)
median(green_building_amenities$Rent)
nrow(green_building_amenities)/nrow(green_building)

non_green_building_amenities = subset(non_green_building, amenities==1)
median(non_green_building_amenities$Rent)
nrow(non_green_building_amenities)/nrow(non_green_building)
```
The median rent is around 2.78 dollars more for green buildings with amenities as compared to non green buildings with amenities. Further, 72.8% of green buildings have amenities, whereas only 51% of non green buildings have amenities. Amenities is therefore a variable that could have affected the higher rent found for green buildings.

```{r}
#age
green_building_age = subset(green_building, age<10)
median(green_building_age$Rent)
hist(green_building_age$Rent)

non_green_building_age = subset(non_green_building, age<10)
median(non_green_building_age$Rent)
hist(non_green_building_age$Rent)
```
Surprisingly, the median rent for green buildings under 10 years old is only 26.75 dollars while the median rent for non green buildings under 10 years old is higher at 29 dollars. This contradicts the the excel guru's conclusions that green buildings have higher rent.

```{r}
 #class 
class_a = subset(green, class_a==1)
class_a_green = subset(green_building,class_a==1)
class_a_non_green = subset(non_green_building,class_a != 1)

class_b = subset(green, class_b==1)
class_b_green = subset(green_building,class_b==1)
class_b_non_green = subset(non_green_building,class_b !=1 )

nrow(class_a_green)/nrow(green_building)
nrow(class_a_non_green)/nrow(non_green_building)

median(class_a$Rent)
median(class_b$Rent)

median(class_a_green$Rent)
median(class_a_non_green$Rent)

median(class_b_green$Rent)
median(class_b_non_green$Rent)
```
A higher proportion of green buildings are class A buildings (80%) than non green (63%).  The median rent for class A is 28.2 dollars per sq ft and the median rent for class B is 24 dollars per sq ft. This is therefore a variable that could have affected the higher rent found for green buildings.

##Bootstrapping
```{r echo=TRUE, message=FALSE, warning=FALSE}
library(mosaic)
library(quantmod)
library(foreach)
setwd('/users/chelseamatthews/Documents')
set.seed(11)
mystocks = c("SPY","TLT","LQD","EEM","VNQ")
myprices = getSymbols(mystocks, from = "2007-01-01")

for(ticker in mystocks) {
	expr = paste0(ticker, "a = adjustOHLC(", ticker, ")")
	eval(parse(text=expr))
}


all_returns =cbind( ClCl(SPYa), ClCl(TLTa),ClCl(LQDa),ClCl(EEMa),ClCl(VNQa))
head(all_returns)

all_returns=as.matrix(na.omit(all_returns))
```

```{r message=FALSE, warning=FALSE}
cor(all_returns)
boxplot(all_returns,main = "Daily Return Dsitribution by Asset Classification",names =c( "SPYa","TLTa","LQDa","EEMa","VNQa"))
summary(all_returns)
```
Looking at the boxplot, it is noticeable that the safest investments are US domestic equities (SPY), investment grade corporate bonds(LQD) and U.S. Treaury bonds (TLT). They have the smallest Inter-quartile ranges (IQR) according to the boxplots. On the other hand, emerging market equities (EEM) and real estate (VNQ) are the riskier investments. They have wider IQRs. This is to be expected becuase emerging markets and real estate are notoriously the most volatile.  Becuase of the risk/return tradeoff, riskier investments have higher potential returns. Investors have to be willing to accept a higher risk of losses, in order to get higher potential returns.

```{r}
pairs(all_returns)
```
SPY and TLT seem to be negatively correlated. SPY has a positive correlation with VNQ. VNQ also has a positive correlation with EEM. LQD has a positive correlation with TLT. Becuase of the negative correlation between SPY and TLT and because of their low variation, they will go in the safe portfolio. The negative correlation means that if one stock goes down, then the other is likely to go up. LQD also has low variation, so it will be the third allocation in the safe profile. EEM nad VNQ will so in the riskier portfolio because they have the most variation and are likely to move together, meaning if they go up, there is large potential profit. On the downside, there are large potential losses if they go down. 

#Even Split
```{r}
#even split
set.seed(11)
return.today = resample(all_returns, 1, orig.ids=FALSE)
initial_wealth = 100000
sim1 = foreach(i=1:5000, .combine='rbind')%do% {
  total_wealth = initial_wealth
  my_weights = c(0.2,0.2,0.2,0.2,0.2)
  holdings = total_wealth*my_weights
  n_days = 20
  wealthtracker = rep(0,n_days)
  for(today in 1:n_days){
    return.today = resample(all_returns,1,orig.ids=FALSE)
    holdings = holdings+holdings*return.today
    total_wealth=sum(holdings)
    wealthtracker[today]=total_wealth
  }
  wealthtracker
}
plot(wealthtracker, type='l')
head(sim1)
hist(sim1[,n_days], 25)



hist(sim1[,n_days]- initial_wealth, main = paste('Histogram even split' ,sep= ' ' ), xlab="Returns" ,breaks=30)
abline(v=mean(sim1[,n_days]-1000),col='red',lwd=2)

quantile(sim1[,n_days], 0.05) - initial_wealth
mean(sim1[,n_days]) 
total_wealth
```
Using the even split portfolio, the most that you will lose is $6,188.87 at a 95% confidence level. In this simulation, the total wealth at the end of the 20 days was $106,258.40 . 


#Safer Portfolio 

For the safer portfolio, we used only LQD, TLT, and SPY since they are the safest investment tolls.They have the least variation, meaning they have a lower chance of causes big losses. Bonds are less vulnerable to stock market fluctuation, allowing their prices to be more constant over-time. The trade-off is that there is a lower change of potential large earnings. From the boxplot we can see that LQD has the lowest variation, so it will be given the biggest weight, to be safer. SPY and TLT seem to be negatively correlated, so we will give them the same weighting of 0.25, in hopes that losses in one is balances from gains in the other. 

```{r}
#safer portfolio

set.seed(11)

initial_wealth = 100000
sim_safe = foreach(i=1:5000, .combine='rbind')%do% {
  total_wealth = initial_wealth
  my_weights = c(0.25,0.25,0.5, 0.0, 0.0)
  holdings = total_wealth*my_weights
  n_days = 20
  wealthtracker = rep(0,n_days)
  for(today in 1:n_days){
    return.today = resample(all_returns,1,orig.ids=FALSE)
    holdings = holdings+holdings*return.today
    total_wealth=sum(holdings)
    wealthtracker[today]=total_wealth
  }
  wealthtracker
}
plot(wealthtracker, type='l')
head(sim_safe)


hist(sim_safe[,n_days]- initial_wealth, main = "Safe Portfolio Histogram",xlab="Returns", breaks=30)
abline(v=mean(sim_safe[,n_days]- initial_wealth), col="red",lwd=2)

mean(sim_safe[,n_days])
quantile(sim1[,n_days], 0.05) - initial_wealth
total_wealth
```
Using the safer portfolio, the most that you will lose is $6,188.87 at a 95% confidence level. In this simulation, the total wealth at the end of the 20 days was $99683.07 . 


#Agressive Portfolio

For the riskier portfolio, only EEM and VNQ were used becuase they were the two riskiest investments.Heavier weight (.6) was given to EEM becuase it is the riskier investment and has the highest varaition. The two instruments are postively correlated. 

```{r}
#riskier portfolio 
set.seed(11)
initial_wealth = 100000

sim_risk = foreach(i=1:5000, .combine='rbind')%do% {
  total_wealth = initial_wealth
  my_weights = c(0.0,0.0,0.0,0.6,0.4)
  holdings = total_wealth*my_weights
  n_days = 20
  wealthtracker = rep(0,n_days)
  for(today in 1:n_days){
    return.today = resample(all_returns,1,orig.ids=FALSE)
    holdings = holdings+holdings*return.today
    total_wealth=sum(holdings)
    wealthtracker[today]=total_wealth
  }
  wealthtracker
}
plot(wealthtracker, type='l')
head(sim_risk)


hist(sim_risk[,n_days]- initial_wealth, main="Riskier Portfolio Histogram",xlab = "Returns", breaks=30)
abline(v=mean(sim_risk[,n_days]-100000),col="red",lwd=2)

mean(sim_risk[,n_days]) 
quantile(sim_risk[,n_days], 0.05) - initial_wealth #how much you lost 
total_wealth
wealthtracker
```

Using the riskier portfolio, the most that you will lose is $12,746.39 at a 95% confidence level. In this simulation, the total wealth at the end of the 20 days was $107,455.50 . 

#Comparing Portfolios 

```{r}
set.seed(11)
names = c("even","safe","risky")
average = c(mean(sim1[,20]),mean(sim_safe[,20]),mean(sim_risk[,20]))
profit_prob = c(sum(sim1[,20]>100000)/5000,
                sum(sim_safe[,20]>100000)/5000,
                sum(sim_risk[,20]>100000)/5000)
Var = c((quantile(sim1[,n_days], 0.05) - initial_wealth), 
         (quantile(sim_safe[,n_days], 0.05) - initial_wealth),
         (quantile(sim_risk[,n_days], 0.05) - initial_wealth)) 
data.frame(names,Var)
```
From the output, you can see that the agressive portfolio is the riskiest, with the largest potential losses. 
